Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity \end{large}

### 2017-01-11 draft.tex
.

After having worked out the analytical basis, we compared the prediction obtained from numerically solving \eqref{NO_equil_cond_interact_matrix_operator} for certain spatial configurations of neurons to the steady-state firing rates of the full spiking network with the same spatial structure. In particular, we were interested in the quality of the predictions in respect to the choice of diffusion constant. Figure \ref{Rand_Matrix_Sol_vs_Sim} shows two examples: For $\mathrm{D=10\, \mu m^2 /s}$, the correlation between measured and predicted firing rates is very good. In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /s}$. Since instant diffusion overrides any spatial inhomogeneities, this represents one limiting case where our analytic model cannot make any predictions. The other limit shown in the plot, $\mathrm{D=0}$, is correctly predicted by the analytic model. However, because of the singularity of the solution, we could not quantify the correlation. Still, both extremes share their property of overriding the effect of spatial heterogeneity onto the firing rates.

\begin{figure}
%% plot_rand_matrix_sol_vs_sim.py
\includegraphics[width=\textwidth]{../../plots/rates_matrix_prediction_vs_sim.png}
\caption{Measured firing rates (t=1200-1500s) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}. For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably "large" diffusion constant of $\mathrm{D=100\, \mu m^2 /s}$.}
\label{Rand_Matrix_Sol_vs_Sim}
\end{figure}

>>>>

After having worked out the analytical basis, we compared the prediction obtained from numerically solving \eqref{NO_equil_cond_interact_matrix_operator} for certain spatial configurations of neurons to the steady-state firing rates of the full spiking network with the same spatial structure. In particular, we were interested in the quality of the predictions in respect to the choice of diffusion constant. Figure \ref{Rand_Matrix_Sol_vs_Sim} shows two examples: For $\mathrm{D=10\, \mu m^2 /s}$, the correlation between measured and predicted firing rates is very good. In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /s}$. Since instant diffusion overrides any spatial inhomogeneities, this represents one limiting case where our analytic model cannot make any predictions. The other limit shown in the plot, $\mathrm{D=0}$, is correctly predicted by the analytic model. However, because of the singularity of the solution, we could not quantify the correlation. Still, both extremes share their property of overriding the effect of spatial heterogeneity onto firing rates. 
%% plot_rand_matrix_sol_vs_sim.py
\includegraphics[width=\textwidth]{../../plots/rates_matrix_prediction_vs_sim.png}
\caption{Measured firing rates (t=1200-1500s) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}. For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably "large" diffusion constant of $\mathrm{D=100\, \mu m^2 /s}$.}
\label{Rand_Matrix_Sol_vs_Sim}
Naturally, these observations led us to the question of how the correlation between predicted measured firing rates behaves in between the aforementioned extremes. Especially, we were interested in the \emph{range} of the diffusion constant for which our model provides a good description of the full spiking network's activity.
